Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
Intro

\begin{abstract}
  In the Dynamic Graph Partitioning problem, we are given a sequence of pairwise communication requests between n nodes, with patterns that may change over time.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated dynamically by migrating nodes between clusters.
  The goal is to devise online algorithms which jointly minimize the amount of inter-cluster communication and migration cost.

  So far, for this natural problem, the best known deterministic algorithm was $O(k^2\cdot \ell^2)$-competitive, and the best known lower bound was $\Omega(k)$ for the competitive ratio of any deterministic algorithm that used the reduction from the caching problem.
  In this paper, we significantly improve this lower bound to $\Omega(k\cdot \ell)$.
  Furthermore, we provide a $O(k\cdot \ell)$-competitive algorithm for the scenario, where the perfect partition of input exists.
\end{abstract}

@@

\section{Introduction}

We study (...) in the scenario where virtual machines can be migrated during runtime to another physical machine.
The possibility of migration allows reacting to unpredictable communication patterns.
If some distant nodes communicate often, it is vital to reduce their distance to save network bandwidth.
The objective is to~minimize the total network bandwidth used for communication and for migration.

@@

Additionally, we contribute to the research on the optimal online algorithm by presenting a $O(k\cdot \ell)$-competitive algorithm for the special case
where the communication graph (i.e., request sequence) admits a \emph{perfect partition},
i.e., a (multi-way) cut of cost zero that is also an optimal partition for the offline problem.
%and every algorithm must colocate every communicating pair.
Note that our $\Omega(k\cdot \ell)$ lower bound generates the input sequence
so that the optimal offline choice is a perfect partition.
%\maciek{Also, it is easy to construct the adversary that forces collocation of requested nodes}
%\mahmoud{this is already the case in the lower bound proof. Do we still need the last sentence here?}
%\maciek{In general it is OK to emphasize some parts of the paper in the intro. %Not sure if this sentence in particular is that important, though.}

\section{Related Work}

In this paper we study the online Balanced RePartitioning problem (formally presented in Section~\ref{sec:problem-definition}).
The static offline version of~the~problem, i.e., a problem variant where
migration is not allowed, and all requests are known in advance is known as the
\emph{$\ell$-balanced graph partitioning problem}. The problem is 
NP-complete, and cannot even be approximated within any finite factor unless P
= NP~\cite{AndRae06}.  The static
variant where $\ell = 2$ corresponds to the minimum bisection problem, which
is already NP-hard~\cite{GaJoSt76}, and 
the currently best approximation ratio is $O(\log n)$~\cite{SarVaz95,ArKaKa99,FeKrNi00,FeiKra02,KraFei06,Raec08}.

@@

\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}

@@

\maciek{We should figure out a better name than "distance". We usually apply two arguments to distance. Examples of names that can be applied to only one configuration as a parameter: radius, span, stretch, spread, width. Also: difference, disparity, distinction, alternation}

>>>>

\begin{abstract}
  In the online Graph RePartitioning problem, we are given a sequence of pairwise communication requests between n nodes, revealed online.
  The objective is to service these requests by partitioning the nodes into $\ell$ clusters, each of size $k$, such that frequently communicating nodes are located in the same cluster.
  The partitioning can be updated by migrating nodes between clusters for a fixed cost.
  The goal is to jointly minimize the amount of inter-cluster communication and migration cost.

  So far, for this natural problem, the best known deterministic algorithm was $O(k^2\cdot \ell^2)$-competitive, and the best known lower bound was $\Omega(k)$ for the competitive ratio of any deterministic algorithm that used the reduction from the caching problem.
  In this paper, we provide the lower bound of $\Omega(k\cdot \ell)$.
  %Furthermore, we provide a $O(k\cdot \ell)$-competitive algorithm for the scenario, where the perfect partition of input exists.
\end{abstract}

@@

\section{Introduction and Related Work}

%We study (...) in the scenario where virtual machines can be migrated during runtime to another physical machine.
%The possibility of migration allows reacting to unpredictable communication patterns.
%If some distant nodes communicate often, it is vital to reduce their distance to save network bandwidth.
%The objective is to~minimize the total network bandwidth used for communication and for migration.

@@

So far, the competitive ratio of the best known algorithm was $O(k^2\cdot \ell^2)$ \cite{repartition-disc}.
We present a $O(k\cdot \ell)$-competitive algorithm for the restricted scenario
where the communication graph (i.e., request sequence) admits a \emph{perfect partition} (i.e., a multi-way cut of cost zero) that is also an optimal partition for the offline problem.
For this setting, the algorithm is optimal, as the lower bound utilized an input sequence that has a perfect partition.

The problem was studied under resource augmentation \cite{repartition-disc}, and under stochastic assumptions of input\maciek{cite}.\maciek{cite other papers that cite DISC?}

The static offline version of~the~problem, called the
\emph{$\ell$-balanced graph partitioning problem} is 
NP-complete, and cannot even be approximated within any finite factor unless P
= NP~\cite{AndRae06}. The static
variant where $\ell = 2$ corresponds to the minimum bisection problem, which
is already NP-hard~\cite{GaJoSt76}, and 
the currently best approximation ratio is $O(\log n)$~\cite{SarVaz95,ArKaKa99,FeKrNi00,FeiKra02,KraFei06,Raec08}.

@@

\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.}

@@
